What is disputed on the web?

### 2010-01-31 papers/wicow_claimfinder/claimfinder.tex
Changes by Barbara

Our tool extracts disputed claims by searching the web for templates such as ``falsely claimed that X'' or ``the myth that X'', and then analysing the parsed sentence structure to identify claims that seem to have the correct form. Given a set of known disputed claims, we can infer further templates by searching for other contexts in which known disputed claims appear.

@@

We believe that ours is the first attempt to automatically acquire a corpus of disputed claims.

@@

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important. The advantage of looking for disputes rather than contradictions is that is is much easier - humans do the hard work of identifying contradictions and deciding whether they are important. The disadvantage of looking for disputes is that this method will only identify contradictions that humans have already identified.

@@

This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, 
textual entailment and contradiction detection. Sentiment analysis aims to determine the attitude 
(usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}. 
Textual entailment is the task of deciding, given two text fragments, whether the meaning of one 
text can be inferred from the other text (add references).

% I think I've folded the stuff from this file into the main body now
%\input{relatedwork.tex}

\section{Finding Disputed Claims}

\x{Include a diagram showing the stages of our dispute finding process}
\maybe{Talk about theories of contrast???}
\maybe{Look at Kehler 2002 on CONTRAST???}

Figure~\ref{not-yet} shows the process we use to build our corpus of disputed claims. 
We find disputed claims by searching the web for for patterns like ``the misconception that $S$'' and ``it is not the case that $S$'' (Section~\ref{searchpattern}). 
For every page that contains the pattern, we grab the raw text from the end of the prefix string, up until the end end of the sentence. We then process each such block of text to filter out any text that does not appear to be a statement (Section~\ref{filterclaim}).

@@

We hand crafted a set of {\bf XX} patterns that indicate that a claim is disputed, such as ``false claim that $X$'' or or ``it is not true that $X$.''

This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
\x{add more related work here}
\todo{add more related work here}

In this work we simply start with an initial set of patterns that we wrote by hand. We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim. From this set of candidate prefix patterns, we manually selected additional patterns. 
\x{add more related work on boostraping here}
\todo{add more related work here}

@@

\subsection{Searching for Claims}
\label{searchpattern}

In order to extract a set of claims, we then search the web for the set of patterns described in the previous session. Rather than building our own search engine, we use the Yahoo BOSS search API~\cite{yahoo-boss}. We search Yahoo BOSS for a raw string such as ``the misconception that'' and then download every web page that Yahoo lists in its search results.
Since we are using an existing search engine, we are limited to searching for simple text strings. This leads us to generate multiple patterns that are almost the same, other than for synonyms. E.g. ``the lie that'' vs ``the deceit that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence. While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, this would be inefficient, since many pages would not contain the pattern.

@@

Since we are interested in the time information on the claims and we want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range. The Yahoo BOSS API does not offer the ability to do so; we thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

@@

From the web pages returned from the search, we form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g. '.','?','!',\texttt{</p>},\texttt{</h1>}, etc). 
\x{it would be quite important to give a sense on the accuracy --precision - of the claims extracted. you can calculated this from a subset of returned candidate claims: out of, say, 100, how many were actually claims?}

@@

\x{Importance of dates}
\x{Work meaning depending on surrounding text}
\x{We do not yet do anything useful with context, but we believe it is important and intend to use it}

@@

\x{Look at a random sample of the data and say how clean it is.}
\x{Evaluate the quality of the claims that we extracted.}
\x{Evaluate the quality of the clusters that we created.}
\x{Evaluate the quality of the different individual templates - which ones have the highest quality claims.}

>>>>

\x{too much emphasis on {\em how}... rewrite following paragrapgh}
Our tool extracts disputed claims by searching the web for templates such as ``falsely claimed that X'' or ``the myth that X'', and then analysing the parsed sentence structure to identify claims that seem to have the correct form. Given a set of known disputed claims, we can infer further templates by searching for other contexts in which known disputed claims appear.

@@

We believe that ours is the first attempt to automatically acquire a corpus of disputed claims from the Web.

@@

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important. The advantage of looking for disputes rather than contradictions is that is is much easier - humans do the hard work of identifying contradictions and deciding whether they are important. 
\x{seems like we do this {\em only} because it's simpler... so perhaps add something around the fact there it's interesting to see where/how/when people disagree... some observation on the social aspects of dispute?}
The disadvantage of looking for disputes is that this method will only identify contradictions that humans have already identified.

@@

This work is also  related to the NLP areas of opinion mining and/or sentiment analysis and textual entailment. Sentiment analysis aims to determine the attitude (usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}. 
Textual entailment is the task of deciding, given two text fragments, whether the meaning of one  text can be inferred from the other text 
\x {add references and say why different}
The methods we use are closely related to related work on information extraction which is the task of identifing and classifing specific semantic entities within documents (i.e. names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.

\section{Finding Disputed Claims}
\label{findingclaims}

\x{Include a diagram showing the stages of our dispute finding process}
\x{BR: I wouldn't... not very informative, I'd think}
\maybe{Talk about theories of contrast???}
\maybe{Look at Kehler 2002 on CONTRAST???}

%Figure~\ref{not-yet} shows the process we use to build our corpus of disputed claims.

We implemented a three stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns (i.e. ``the misconception that'' and ``it is not the case that''). We then search the Web for these patterns and finally process the text of the returned Web pages to extract only the parts that describe the disputed claims.

@@

We hand crafted a set of {\bf XX} patterns that we hypothesize may  indicate that a claim is disputed, such as ``false claim that'' or or ``it is not true that.''

This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These methods differ on how {\bf finish here}
\x{add more related work here}
\todo{add more related work here}

In this work we simply start with an initial set of patterns that we wrote by hand. We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim. From this set of candidate prefix patterns, we manually selected additional patterns.

\x{add more related work on boostraping here, adding differences}
\todo{add more related work here}

@@

\subsection{Searching the Web for Claims}
\label{searchpattern}

We then search the web for the set of patterns described in the previous session. Rather than building our own search engine, we use the Yahoo BOSS search API~\cite{yahoo-boss}. We search Yahoo BOSS for a raw string such as ``the misconception that'' and then download every web page that Yahoo lists in its search results.
Since we are using an existing search engine, we are limited to searching for simple text strings. This leads us to generate multiple patterns that are almost the same, other than for synonyms. E.g. ``the lie that'' vs ``the deceit that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence. While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, this would be inefficient, since many pages would not contain the pattern.

@@

Since we are interested in the time information of the claims and we want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range. The Yahoo BOSS API does not offer the ability to do so; we thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

@@

From the web pages returned from the search, we form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g. '.','?','!',\texttt{</p>},\texttt{</h1>}, etc).

\x{it would be quite important to give a sense on the accuracy --precision - of the claims extracted. you can calculated this from a subset of returned candidate claims: out of, say, 100, how many were actually claims?}

@@

\x{Importance of dates}
\x{Work meaning depending on surrounding text}
\x{We do not yet do anything useful with context, but we believe it is important and intend to use it}
\x{context can be surrounding text but also features of the web pages -- domain,  "authority," in-links, format; context is also the author: expert? social info on author...}

@@

\x{Look at a random sample of the data and say how clean it is.}
\x{Evaluate the quality of the claims that we extracted.}
\x{Evaluate the quality of the clusters that we created.}
\x{Evaluate the quality of the different individual templates - which ones have the highest quality claims.}
\x{say something about {\em duplicate} claims?}
